The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-02 exp-resurgence.tex
Move statement that convolution preserves holomorphic L-infinity space

@@

We just need to prove that
\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}] \]
\textbf{A} \textbf{V} [Find and prove correct statement. Maybe it should be\ldots]
\[ \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}] = \laplace_{\zeta_\alpha,0}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
\begin{todo}[Add proof for $\alpha\neq 0$.]\end{todo}
\item \begin{align*}
\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & \defeq \left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta \right)\left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \psi\,d\zeta \right) \\
& = \left( \int_{\mathcal{J}_{\zeta', \alpha}^\theta} e^{-z\zeta'} \phi'\,d\zeta' \right)\left( \int_{\mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta''} \psi''\,d\zeta'' \right) \\
& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;d\zeta' \wedge d\zeta''.
\item Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \begin{todo}[with $\zeta' + \zeta'' = \zeta$]\end{todo}
\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;(d\zeta' + d\zeta'') \wedge d\zeta'' \\
& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta}\,\phi'\,\psi''\;d\zeta \wedge d\zeta'' \\
& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} \big(e^{-z\zeta}\;d\zeta\big) \wedge \big(\phi'\,\psi''\;d\zeta''\big) \\
& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \left(\int_{\substack{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\;d\zeta''\right) d\zeta \\
& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta}\,(\phi \ast_{\zeta, \alpha} \psi)\;d\zeta \\
& = \laplace^\theta_{\zeta, \alpha}(\phi \ast_{\zeta, \alpha} \psi).
\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}](a)&= \int_{\mathcal{J}^\theta_{\zeta, \alpha}} e^{-z\zeta(a)} \left(\int_{\zeta=\alpha}^a \psi \mathsf{R}^*\phi\;d\zeta\right)\;d\zeta

\begin{align*}
\laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}]&=\int_\alpha^\infty e^{-z t}\phi(t)dt \int_\alpha^\infty e^{-z u} \psi(u) du \\
&=\int_\alpha^\infty \left(\int_\alpha^\infty  e^{-z (t+u)}\phi(t) \psi(u) du \right)dt \\
&=\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
\end{align*}
Define $\psi(s)=0$ if $s<\alpha$, thus $\psi(s-t)=0$ if $s<t+\alpha$, 
\begin{align*}
\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
\end{align*}
Under the assumption that the integral is absolutely convergent, we can exchange the order of integration
\begin{align*}
\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^\infty    \psi(s-t) \phi(t) dt \right)ds\\
&=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^s    \psi(s-t) \phi(t) dt \right)ds \\
&=\int_\alpha^\infty e^{-z s} \phi\ast_{t,\alpha}\psi ds 
\end{align*}
\textcolor{orange}{See Theorem 5.25 of \cite{diverg-resurg-i}}
\end{verify}
\end{proof}
%
\begin{remark}
For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[Add coordinate to $\ast$ elsewhere too]\end{todo}, following the standard convention.   
\end{remark}
Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).

\begin{revised}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.\end{revised} \begin{todo}Write more if needed, and also make sure it's actually correct. The old text below has mistakes.\end{todo}
\begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
\begin{todo}[actually need $\Omega_0$ in lemma]\end{todo}
\begin{lemma}
If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \begin{todo}[no; revise]\end{todo} under the convolution product $\ast_{\zeta, \alpha}$.
\textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
\end{lemma}
\begin{proof}
Suppose $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. The convolution integral
\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,|d\zeta| \]
can then always be evaluated along the path $\zeta = (1-t)\,\alpha + t\,\zeta(a)$ parameterized by $t \in (0, 1)$.

@@

&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\

@@

In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}. 
\begin{definition}
For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =\alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
where $p$ is any point on the position domain $B$. \begin{todo}[If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above? Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
% \begin{equation*}
%     \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi \, d\zeta_\alpha.
% \end{equation*}
% }
\end{definition}
The fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[Equation 35]{mladenov2014advanced}.

>>>>

\begin{todo}[Show that Laplace transform preserves domain of Laplace transform]\end{todo}
\begin{draft}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$. The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta, 0}$.\end{draft}

@@

For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[Add coordinate to $\ast$ elsewhere too]\end{todo}, following the standard convention.   
Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).

\begin{todo}Move before calculation of Laplace transform of convolution, write more if needed, and also make sure it's actually correct. The old text below has mistakes.\end{todo}
\begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
\begin{todo}[actually need $\Omega_0$ in lemma]\end{todo}
\begin{lemma}
If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \begin{todo}[no; revise]\end{todo} under the convolution product $\ast_{\zeta, \alpha}$.
\textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
\end{lemma}
\begin{proof}
Suppose $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. The convolution integral
\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,|d\zeta| \]
can then always be evaluated along the path $\zeta = (1-t)\,\alpha + t\,\zeta(a)$ parameterized by $t \in (0, 1)$.

@@

&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\

@@

In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}. 
\begin{definition}
For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =\alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
where $p$ is any point on the position domain $B$. \begin{todo}[\textbf{V} If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above? Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
% \begin{equation*}
%     \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi \, d\zeta_\alpha.
% \end{equation*}
% }
\end{definition}
The fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
\begin{align*}
\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0),
\end{align*}
and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[Equation 35]{mladenov2014advanced}.
